# Data

This chapter contains the preparation of the data for the replication of the empirical analysis of @Juselius2006Cointegrated.

## Load Data

Download the material for the textbook provided by [Estima](https://www.estima.com/).

The material for the replication of the empirical analysis can be downloaded from the world wide web.

1) Download the material [here](https://www.estima.com/cointhandbook/CointegratedVARModelHandbook.zip).
2) Unpack the material in your directory.
3) Load the data stored in the file `book.xls`.

<!-- https://www.estima.com/cointhandbook/CointegratedVARModelHandbook.zip -->

<!-- See: [RATS Handbook for The Cointegrated VAR Model](https://www.estima.com/textbook_juselius.shtml) -->



```{r, warning=FALSE, message=FALSE}

# Load data
library(readxl)
data <- read_excel("./CointegratedVARModelHandbook/book.xls")
data <- data[,colnames(data)[-1]]

```

Define the number of observations and a time variable.

```{r}

# Number of observations
TT <- nrow(data)

# Define time variable
data$time <- seq(as.Date("1973-01-01"), as.Date("2003-01-01"), by="quarter")

```

The data span observations from *1973-Q1* to *2003-Q1*.

## Dummy Variables

Construct the dummy variables.

Define *"transitory intervention" dummy* at *1975-Q4*.

```{r}

# Create "transitory intervention" dummy at 1975:4
data$Dt754 <- rep(0,TT)
data$Dt754[which(data$time == as.Date("1975-10-01"))] <- 1
data$Dt754[which(data$time == as.Date("1976-01-01"))] <- -0.5
data$Dt754[which(data$time == as.Date("1976-04-01"))] <- -0.5

```

Define *"permanent intervention" dummy* at *1976-Q4*.

```{r}

# Create "permanent intervention" dummy at 1976:4
data$Dp764 <- rep(0,TT)
data$Dp764[which(data$time == as.Date("1976-10-01"))] <- 1

```

Define *"mean shift" dummy* at *1983-Q1*.

```{r}

# Create "mean shift" dummy at 1983:1
data$Ds831 <- rep(0,TT)
data$Ds831[which(data$time %in% seq(as.Date("1983-01-01"), as.Date("2003-01-01"), by="quarter"))] <- 1

```

Define difference of *"mean shift" dummy*, i.e., *"permanent intervention" dummy* at *1983-Q1*.

```{r}

# Create difference of "mean shift" dummy, i.e., "permanent intervention" dummy, at 1983:1
data$Dp831 <- rep(0,TT)
data$Dp831[which(data$time == as.Date("1983-01-01"))] <- 1

```

Define lag of *"permanent intervention" dummy* at *1983-Q1*, i.e., *"permanent intervention" dummy* at *1983-Q2*.

```{r}

# Define lag of "permanent intervention" dummy, at 1983:1
data$Dp832 <- rep(0,TT)
data$Dp832[which(data$time == as.Date("1983-04-01"))] <- 1

```
