# The Cointegrated VAR

```{r, include=FALSE}

source("./R/01-data.R")

```

This chapter contains the replication of the material of Chapter 7 of @Juselius2006Cointegrated.

## Estimation

Load the function `ca_jo_jus06_fun()` from *GitHub*. 

```{r}

source("https://raw.githubusercontent.com/mmoessler/juselius-2006/main/R/ca_jo_jus06_fun.R")

```

Call the function `ca_jo_jus06_fun()` for the Danish data.



Include *dummies* `Dt754`, `Dp764` and `Dp831` unrestricted.

Include *dummy* `Ds831` restricted to the cointegrating relationship.

Estimation *with trend in the cointegrating relationship*, i.e., call `ca_jo_jus06_fun(()` with `ecdet = c("trend")`.

```{r}

# with trend in cir, with shift dummy and with Ds831 in cir
ca.jo.res.01 <- ca_jo_jus06_fun(x = data[,c("Lm3rC","Lyr","Dpy","Rm","Rb")], type = c("trace"), ecdet = c("trend"), K = 2, spec = c("transitory"), data = data)

```

Estimation *without trend in the cointegrating relationship*, i.e., call `ca_jo_jus06_fun(()` with `ecdet = c("none")`.

```{r}

# without trend in cir, with shift dummy and with Ds831 in cir
ca.jo.res.02 <- ca_jo_jus06_fun(x = data[,c("Lm3rC","Lyr","Dpy","Rm","Rb")], type = c("trace"), ecdet = c("none"), K = 2, spec = c("transitory"), data = data)

```

Note, the function `ca_jo_jus06_fun()` is based on the function `ca.jo()` from the library `urca` (see also @Pfaff2008Analysis). The dummy variables are added inside the function, i.e., "hard". Check the code on *GitHub* (`mmoessler/juselius-2006/main/R/ca_jo_jus06_fun.R`) for more information.

## Results

Lambdas $\widehat{\lambda}_i$ (see *Table 7.1* of @Juselius2006Cointegrated)

```{r}

round(Re(ca.jo.res.01$lambda), 2) 

```

Non-nomralized eigenvectors $\widehat{v}_i$ (see *Table 7.1* of @Juselius2006Cointegrated)

```{r}

round(Re(ca.jo.res.01$Vorg), 2)

```

Normalized eigenvectors $\widehat{\beta}_i$ (see *Table 7.1* of @Juselius2006Cointegrated)

```{r}

V.01 <- cbind(cbind(ca.jo.res.01$Vorg[,1]/ca.jo.res.01$Vorg[3,1]),
              cbind(ca.jo.res.01$Vorg[,2]/ca.jo.res.01$Vorg[1,2]),
              cbind(ca.jo.res.01$Vorg[,3]/ca.jo.res.01$Vorg[4,3]),
              cbind(ca.jo.res.01$Vorg[,4]/ca.jo.res.01$Vorg[2,4]),
              cbind(ca.jo.res.01$Vorg[,5]/ca.jo.res.01$Vorg[5,5]),
              cbind(ca.jo.res.01$Vorg[,6]/ca.jo.res.01$Vorg[1,6]),
              cbind(ca.jo.res.01$Vorg[,7]/ca.jo.res.01$Vorg[1,7]))

round(V.01, 2)

```

Normalized weights $\widehat{\alpha}_i$ (see *Table 7.1* of @Juselius2006Cointegrated)


```{r}

W.01 <- ca.jo.res.01$S0K %*% V.01 %*% solve(t(V.01) %*% ca.jo.res.01$SKK %*% V.01)

round(W.01, 2)

```

Combined effects: $\widehat{\Pi}$ (see *Table 7.1* of @Juselius2006Cointegrated)

```{r}

round(ca.jo.res.01$PI, 2)

```




