# The Cointegrated VAR

```{r, include=FALSE}

source("./R/01-data.R")

```

This chapter contains the replication of the material of Chapter 5 of @Juselius2006Cointegrated.

## Estimation

Load the function `ca_jo_jus06_fun()` from *GitHub*. 

```{r}

source("https://raw.githubusercontent.com/mmoessler/juselius-2006/main/R/ca_jo_jus06_fun.R")

```

Call the function `ca_jo_jus06_fun()` for the Danisch data.



Include *dummies* `Dt754`, `Dp764` and `Dp831` unrestricted.

Include *dummy* `Ds831` restricted to the cointegrating relationship.

Estimation *with trend in the cointegrating relationship*, i.e., call `ca_jo_jus06_fun(()` with `ecdet = c("trend")`.

```{r}

# with trend in cir, with shift dummy and with Ds831 in cir
ca.jo.res.01 <- ca_jo_jus06_fun(x = data[,c("Lm3rC","Lyr","Dpy","Rm","Rb")], type = c("trace"), ecdet = c("trend"), K = 2, spec = c("transitory"), data = data)

```

Estimation *without trend in the cointegrating relationship*, i.e., call `ca_jo_jus06_fun(()` with `ecdet = c("none")`.

```{r}

# without trend in cir, with shift dummy and with Ds831 in cir
ca.jo.res.02 <- ca_jo_jus06_fun(x = data[,c("Lm3rC","Lyr","Dpy","Rm","Rb")], type = c("trace"), ecdet = c("none"), K = 2, spec = c("transitory"), data = data)

```

