# Testing Restrictions on $\beta$

```{r, include=FALSE}

source("./R/01-data.R")
source("./R/03-cointegrated-var.R")

```

This chapter contains the replication of the material of Chapter 10 of @Juselius2006Cointegrated.


<!-- .................................................. -->
<hr>

## Formulating hypotheses as restrictions on $\beta$

<span style="font-size: 18pt">1) </span><span style="font-size: 18pt; text-decoration: underline">Long-run *money demand* relationship</span>:

<span style="font-size: 16pt">1.1) Formulated in terms of *free parameters*</span>

\begin{align*}
{\bf \beta}_1 &= {\bf \text{H}}_1 {\bf \varphi}_1 \\
&= \begin{bmatrix}
\phantom{-}1 & \phantom{-}0 & \phantom{-}0 \\
-1 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}1 & \phantom{-}0 \\
\phantom{-}0 & -1 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}1
\end{bmatrix}
\begin{bmatrix}
\varphi_{11} \\
\varphi_{12} \\
\varphi_{13}
\end{bmatrix}
\end{align*}

```{r}

H1 <- matrix(c( 1 , 0, 0,
               -1,  0, 0,
                0 , 0, 0,
                0,  1, 0,
                0, -1, 0,
                0,  0, 1), c(6, 3), byrow = TRUE)
H1

```

<span>1.2) Formulated in terms of *restricted parameters*</span>

\begin{align*}
{\bf \text{R}}_1^{'} {\bf \beta}_1 &=  {\bf 0} \\
\begin{bmatrix}
\phantom{-}1 & \phantom{-}1 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}1 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}1 & \phantom{-}1 & \phantom{-}0
\end{bmatrix}
\begin{bmatrix}
\beta_{11} \\
\beta_{12} \\
\beta_{13} \\
\beta_{14} \\
\beta_{15} \\
\beta_{16}
\end{bmatrix}
&=
\begin{bmatrix}
0 \\
0 \\
0
\end{bmatrix}
\end{align*}

```{r}

R1 <- t(matrix(c( 1, 1, 0, 0, 0, 0,
                  0, 0, 1, 0, 0, 0,
                  0, 0, 0, 1, 1, 0), c(3, 6), byrow = TRUE))
t(R1)

```

<span>1.3) Relationship between specification in terms of *free* and *restricted parameters*</span>

* ${\bf \text{R}}_i = {\bf \text{H}}_{\perp,i}$, i.e., ${\bf \text{R}}_i^{'} {\bf \text{H}}_{i} = {\bf 0}$

```{r}

t(R1) %*% H1

```

* ${\bf \text{H}}_i$ lies in the left nullspace of ${\bf \text{R}}_i$, i.e.,  ${\bf \text{H}}_i = {\bf N} \left( {\bf \text{R}}_i^{'} \right)$

```{r}

H1x <- MASS::Null(R1)
H1x

H1

```

Note, the condition above identifies only the space on which ${\bf \text{H}}_i$ lies. The particular 

```{r}

round(cbind(H1x[,1,drop=FALSE] + H1x[,2,drop=FALSE], H1x[,1,drop=FALSE] - H1x[,2,drop=FALSE], H1x[,3,drop=FALSE]), 3)

H1

```

```{r, include=FALSE}

norm(H1x, type = "2")

```



<span style="font-size: 18pt">2) </span><span style="font-size: 18pt; text-decoration: underline">Long-run *aggregate demand* relationship</span>:

<span style="font-size: 16pt">2.1) Formulated in terms of *free parameters*</span>

\begin{align*}
{\bf \beta}_2 &= {\bf \text{H}}_2 {\bf \varphi}_2 \\
&= \begin{bmatrix}
\phantom{-}0 & \phantom{-}0 \\
\phantom{-}1 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}1 \\
\phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & -1 \\
\phantom{-}0 & \phantom{-}0
\end{bmatrix}
\begin{bmatrix}
\varphi_{21} \\
\varphi_{22}
\end{bmatrix}
\end{align*}

```{r}

H2 <- matrix(c( 0,  0,
                1,  0,
                0 , 1,
                0,  0,
                0, -1,
                0,  0), c(6, 2), byrow = TRUE)
H2

```

<span style="font-size: 16pt">2.2) Formulated in terms of *restricted parameters*</span>

\begin{align*}
{\bf \text{R}}_2^{'} {\bf \beta}_2 &=  {\bf 0} \\
\begin{bmatrix}
\phantom{-}1 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}1 & \phantom{-}0 & \phantom{-}1 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}1 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}1
\end{bmatrix}
\begin{bmatrix}
\beta_{21} \\
\beta_{22} \\
\beta_{23} \\
\beta_{24} \\
\beta_{25} \\
\beta_{26}
\end{bmatrix}
&=
\begin{bmatrix}
0 \\
0 \\
0 \\
0
\end{bmatrix}
\end{align*}

```{r}

R2 <- t(matrix(c( 1, 0, 0, 0, 0, 0,
                  0, 0, 1, 0, 1, 0,
                  0, 0, 0, 1, 0, 0,
                  0, 0, 0, 0, 0, 1), c(4, 6), byrow = TRUE))
t(R2)

```

<span style="font-size: 16pt">2.3) Relationship between specification in terms of *free* and *restricted parameters*</span>

* ${\bf \text{R}}_i = {\bf \text{H}}_{\perp,i}$, i.e., ${\bf \text{R}}_i^{'} {\bf \text{H}}_{i} = {\bf 0}$

```{r}

t(R2) %*% H2

```

* ${\bf \text{H}}_i$ lies in the left nullspace of ${\bf \text{R}}_i$, i.e.,  ${\bf \text{H}}_i = {\bf N} \left( {\bf \text{R}}_i^{'} \right)$

```{r}

H2x <- MASS::Null(R2)
H2x

H2

```

Note, the condition above identifies only the space on which ${\bf \text{H}}_i$ lies. The particular 

```{r}

round(cbind((H2x[,1,drop=FALSE] + H2x[,2,drop=FALSE]) / (H2x[2,1] + H2x[2,2]), (H2x[,2,drop=FALSE] - H2x[,1,drop=FALSE])), 3)

H2

```



<span style="font-size: 18pt">3) </span><span style="font-size: 18pt; text-decoration: underline">Long-run *term structure* relationship</span>:

<span style="font-size: 16pt">3.1) Formulated in terms of *free parameters*</span>

\begin{align*}
{\bf \beta}_3 &= {\bf \text{H}}_3 {\bf \varphi}_3 \\
&= \begin{bmatrix}
\phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 \\
\phantom{-}1 & \phantom{-}0 \\
-1 & -1 \\
\phantom{-}0 & \phantom{-}1
\end{bmatrix}
\begin{bmatrix}
\varphi_{31} \\
\varphi_{32}
\end{bmatrix}
\end{align*}

```{r}

H3 <- matrix(c( 0,  0,
                0,  0,
                0 , 0,
                1,  0,
               -1,  0,
                0,  1), c(6, 2), byrow = TRUE)
H3

```

<span style="font-size: 16pt">3.2) Formulated in terms of *restricted parameters*</span>

\begin{align*}
{\bf \text{R}}_2^{'} {\bf \beta}_2 &=  {\bf 0} \\
\begin{bmatrix}
\phantom{-}1 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}1 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}1 & \phantom{-}0 & \phantom{-}0 & \phantom{-}0 \\
\phantom{-}0 & \phantom{-}0 & \phantom{-}0 & \phantom{-}1 & \phantom{-}1 & \phantom{-}0
\end{bmatrix}
\begin{bmatrix}
\beta_{21} \\
\beta_{22} \\
\beta_{23} \\
\beta_{24} \\
\beta_{25} \\
\beta_{26}
\end{bmatrix}
&=
\begin{bmatrix}
0 \\
0 \\
0 \\
0
\end{bmatrix}
\end{align*}

```{r}

R3 <- t(matrix(c( 1, 0, 0, 0, 0, 0,
                  0, 1, 0, 0, 0, 0,
                  0, 0, 1, 0, 0, 0,
                  0, 0, 0, 1, 1, 0), c(4, 6), byrow = TRUE))
t(R3)

```

<span style="font-size: 16pt">3.3) Relationship between specification in terms of *free* and *restricted parameters*</span>

* ${\bf \text{R}}_i = {\bf \text{H}}_{\perp,i}$, i.e., ${\bf \text{R}}_i^{'} {\bf \text{H}}_{i} = {\bf 0}$

```{r}

t(R3) %*% H3

```

* ${\bf \text{H}}_i$ lies in the left nullspace of ${\bf \text{R}}_i$, i.e.,  ${\bf \text{H}}_i = {\bf N} \left( {\bf \text{R}}_i^{'} \right)$

```{r}

H3x <- MASS::Null(R3)
H3x

H3

```

Note, the condition above identifies only the space on which ${\bf \text{H}}_i$ lies. The particular 

```{r}

round(cbind(H3x[,1,drop=FALSE] / H3x[4,1], H3x[,2,drop=FALSE]), 3)

H3

```



<!-- .................................................. -->
<hr>

## Same restrictions on all $\beta$

Load the function `ca_jo_jus06_hr3_fun()` from *GitHub*. 

```{r}

source("https://raw.githubusercontent.com/mmoessler/juselius-2006/main/R/blrtest_fun.R")

```

Note, the function `blrtest_fun()` is based on the function `blrtest()` from the library `urca` (see also @Pfaff2008Analysis) and edited such that it is compatible with the results from the function `ca_jo_jus06_fun`.

### $\mathcal{H}_1$

$\mathcal{H}_1$: $\beta_{trend}=0$

```{r}

ca.jo.res.01$P <- 6
z <- ca.jo.res.01
r <- 3

# exclusion of trend in cir
H1 <- matrix(c(1,0,0,0,0,0,
               0,1,0,0,0,0,
               0,0,1,0,0,0,
               0,0,0,1,0,0,
               0,0,0,0,1,0,
               0,0,0,0,0,1,
               0,0,0,0,0,0), nrow=7, ncol=6, byrow=T)

b.h01.res <- blrtest_fun(z = z, H = H1, r = r)

# test results
b.h01.res$teststat
b.h01.res$pval

# restricted cointegrating vectors
round(b.h01.res$V[,1]/b.h01.res$V[3,1], 2)
round(b.h01.res$V[,2]/b.h01.res$V[1,2], 2)
round(b.h01.res$V[,3]/b.h01.res$V[4,3], 2)

```

### $\mathcal{H}_2$

$\mathcal{H}_2$: $\beta_{D_S831}=0$

```{r}

ca.jo.res.01$P <- 6
z <- ca.jo.res.01
r <- 3

# exclusion of shift in cir
H2 <- matrix(c(1,0,0,0,0,0,
               0,1,0,0,0,0,
               0,0,1,0,0,0,
               0,0,0,1,0,0,
               0,0,0,0,1,0,
               0,0,0,0,0,0,
               0,0,0,0,0,1), nrow=7, ncol=6, byrow=T)

b.h02.res <- blrtest_fun(z = z, H = H2, r = r)

# test results
b.h02.res$teststat
b.h02.res$pval

# restricted cointegrating vectors
round(b.h02.res$V[,1]/b.h02.res$V[3,1], 2)
round(b.h02.res$V[,2]/b.h02.res$V[1,2], 2)
round(b.h02.res$V[,3]/b.h02.res$V[4,3], 2)

```

### $\mathcal{H}_3$

$\mathcal{H}_3$: $\beta_{m^{r}}=-\beta_{y^{r}}$

```{r}

ca.jo.res.01$P <- 6
z <- ca.jo.res.01
r <- 3

# exclusion of shift in cir
H3 <- matrix(c( 1,0,0,0,0,0,
               -1,0,0,0,0,0,
                0,1,0,0,0,0,
                0,0,1,0,0,0,
                0,0,0,1,0,0,
                0,0,0,0,1,0,
                0,0,0,0,0,1), nrow=7, ncol=6, byrow=T)
H3

b.h03.res <- blrtest_fun(z = z, H = H3, r = r)

b.h03.res$teststat
b.h03.res$pval

b.h03.res$V

round(b.h03.res$V[,1]/b.h03.res$V[3,1], 3)
round(b.h03.res$V[,2]/b.h03.res$V[1,2], 3)
round(b.h03.res$V[,3]/b.h03.res$V[4,3], 3)

```
### $\mathcal{H}_4$

$\mathcal{H}_4$: $\beta_{R_{m}}=-\beta_{R_{b}}$

```{r}

ca.jo.res.01$P <- 6
z <- ca.jo.res.01
r <- 3

# exclusion of shift in cir
H4 <- matrix(c( 1,0,0, 0,0,0,
                0,1,0, 0,0,0,
                0,0,1, 0,0,0,
                0,0,0, 1,0,0,
                0,0,0,-1,0,0,
                0,0,0, 0,1,0,
                0,0,0, 0,0,1), nrow=7, ncol=6, byrow=T)
H4

b.h04.res <- blrtest_fun(z = z, H = H4, r = r)

b.h04.res$teststat
b.h04.res$pval

b.h04.res$V

round(b.h04.res$V[,1]/b.h04.res$V[3,1], 3)
round(b.h04.res$V[,2]/b.h04.res$V[1,2], 3)
round(b.h04.res$V[,3]/b.h04.res$V[4,3], 3)

```

### $\mathcal{H}_5$

$\mathcal{H}_5$: $\beta_{m^{r}}=-\beta_{y^{r}}$ and $\beta_{trend}=0$

```{r}

ca.jo.res.01$P <- 6
z <- ca.jo.res.01
r <- 3

# exclusion of shift in cir
H5 <- matrix(c( 1,0,0, 0,0,
               -1,0,0, 0,0,
                0,1,0, 0,0,
                0,0,1, 0,0,
                0,0,0, 1,0,
                0,0,0, 0,1,
                0,0,0, 0,0), nrow=7, ncol=5, byrow=T)
H5

b.h05.res <- blrtest_fun(z = z, H = H5, r = r)

b.h05.res$teststat
b.h05.res$pval

b.h05.res$V

round(b.h05.res$V[,1]/b.h05.res$V[3,1], 3)
round(b.h05.res$V[,2]/b.h05.res$V[1,2], 3)
round(b.h05.res$V[,3]/b.h05.res$V[4,3], 3)

```

### $\mathcal{H}_6$

$\mathcal{H}_6$: $\beta_{m^{r}}=-\beta_{y^{r}}$, $\beta_{R_{m}}=-\beta_{R_{b}}$ and $\beta_{trend}=0$

```{r}

ca.jo.res.01$P <- 6
z <- ca.jo.res.01
r <- 3

H6 <- matrix(c( 1,0, 0, 0,
               -1,0, 0, 0,
                0,1, 0, 0,
                0,0, 1, 0,
                0,0,-1, 0,
                0,0, 0, 1,
                0,0, 0, 0), nrow=7, ncol=4, byrow=T)
H6

b.h06.res <- blrtest_fun(z = z, H = H6, r = r)

b.h06.res$teststat
b.h06.res$pval

b.h06.res$V

round(b.h06.res$V[,1]/b.h06.res$V[3,1], 3)
round(b.h06.res$V[,2]/b.h06.res$V[1,2], 3)
round(b.h06.res$V[,3]/b.h06.res$V[4,3], 3)

```
