---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Identification of the long-run structure

```{r, include=FALSE}

source("./R/01-data.R")
source("./R/03-cointegrated-var.R")

```

This chapter contains the replication of the material of Chapter 12 of @Juselius2006Cointegrated.

## Just-identified long-run structures

### $\mathcal{H}_{S.1}$

Use the estimation result `ca.jo.res.02` and reorder the variables according to $\left(m^r, \Delta p, R_m, y^r, R_b\right)$.

```{r}

P <- matrix(c(1,0,0,0,0,0,
              0,0,1,0,0,0,
              0,0,0,1,0,0,
              0,1,0,0,0,0,
              0,0,0,0,1,0,
              0,0,0,0,0,1), nrow = 6, byrow = T)

beta.hat <- P %*% ca.jo.res.02$Vorg[,c(1,2,3)]

alpha.hat <- P[-6,-6] %*% ca.jo.res.02$Worg[,c(1,2,3)]

```

Apply triangularization, i.e., normalize w.r.t. to $m^r$, $\Delta p$ and $R_m$.

```{r}

r <- 3
S1 <- diag(r)
S2 <- matrix(0, nrow = nrow(beta.hat) - r, ncol = r)
S <- rbind(S1, S2)

```

```{r}

beta.norm <- beta.hat %*% solve(t(S) %*% beta.hat)

```

$\widehat{\beta}_i$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(beta.norm, 2)

```

```{r}

alpha.norm <- alpha.hat %*% (t(beta.hat) %*% S)

```

$\widehat{\alpha}_i$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(alpha.norm, 2)

```

Construct standard errors using *Equation 12.13* of @Juselius2006Cointegrated.

Reorder the elements in $S_{11}$ and $\widehat{\Omega}$ according to $\left(m^r, \Delta p, R_m, y^r, R_b\right)$.

```{r}

S11 <- P %*% ca.jo.res.02$SKK %*% t(P)

```

```{r}

Sig.e <- P[-6,-6] %*% ca.jo.res.02$DELTA %*% t(P[-6,-6])

```

```{r}

TT <- nrow(ca.jo.res.02$R0)
nr <- nrow(beta.norm)

library(MASS)
H <- Null(S)
H <- diag(r) %x% H
cov.beta.jus <- H %*% solve( t(H) %*% ( (t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) %x% S11 ) %*% H ) %*% t(H) / TT

```

```{r}

se <- sqrt(diag(cov.beta.jus)[c((0*nr+r+1):(0*nr+r+r), (1*nr+r+1):(1*nr+r+r), (2*nr+r+1):(2*nr+r+r))])
be <- rbind(beta.norm[(r+1):nr, 1, drop = FALSE], beta.norm[(r+1):nr, 2, drop = FALSE], beta.norm[(r+1):nr, 3, drop = FALSE])

te <- be/se

```

Test statistic $\widehat{\beta}_i$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(te, 2)

```


