---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Identification of the long-run structure

```{r, include=FALSE}

source("./R/01-data.R")
source("./R/03-cointegrated-var.R")

```

This chapter contains the replication of the material of Chapter 12 of @Juselius2006Cointegrated.



<!-- .................................................. -->
<hr>

## Just-identified long-run structures

Load the function `ca_jo_jus06_hr3_fun()` from *GitHub*. 

```{r}

source("https://raw.githubusercontent.com/mmoessler/juselius-2006/main/R/ca_jo_jus06_hr3_fun.R")

```

Note, the function `ca_jo_jus06_hr3_fun()` is based on the function `bh6lrtest()` from the library `urca` (see also @Pfaff2008Analysis) and extended such that restriction can be imposed on each of the three cointegrating relationships individually.

Thus, the switching algorithm proposed by @JohansenJuselius1992Testing is applied by iterating over all three cointegrating relationships. This allows us to estimate just-identified and over-identified long-run structures as in Chapter 12.

Check the code on *GitHub* (`mmoessler/juselius-2006/main/R/ca_jo_jus06_fun.R`) for more information.

<!-- .................................................. -->
<hr>

### $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated

Construct the design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 0, 0,
                0, 0, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = TRUE)

H2 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = TRUE)

H3 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = TRUE)

```

Estimate the (just) identified cointegrating and adjustment coefficients.

```{r}

z <- ca.jo.res.02
# z$P <- 6

b.s1.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 4)

```

Compare results for $\widehat{\beta}$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

beta.norm <- b.s1.res$V
round(beta.norm, 2)

```

Compare results for $\widehat{\alpha}$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

alpha.norm <- b.s1.res$W
round(alpha.norm, 2)

```

Compute standard error for $\widehat{\beta}$

```{r}

H <- matrix(rep(0, (3*6)*(3*4-3)), nrow = (3*6), ncol = (3*4-3))

H[( 0+1): 6,(0+1):3] <- H1[,-1]
H[( 6+1):12,(3+1):6] <- H2[,-2]
H[(12+1):18,(6+1):9] <- H3[,-2]

```

```{r}

Sig.e <- b.s1.res$z$DELTA
S11   <- b.s1.res$z$SKK

TT <- nrow(b.s1.res$z$R0)

```

```{r}

cov.beta <- H %*% solve( t(H) %*% ( (t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) %x% S11 ) %*% H ) %*% t(H) / TT

```

Compare with standard error for $\widehat{\beta}$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

matrix(round(c(beta.norm)/sqrt(diag(cov.beta)), 2), nrow = 6, ncol = 3)

```

Compute standard error for $\widehat{\alpha}$

```{r, include=FALSE}

cov.alpha.11 <- Sig.e[1,1] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[1,1] / TT
cov.alpha.11 # (1)

cov.alpha.12 <- Sig.e[1,1] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[2,2] / TT
cov.alpha.12 # (2)

cov.alpha.13 <- Sig.e[1,1] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[3,3] / TT
cov.alpha.13 # (3)


cov.alpha.21 <- Sig.e[2,2] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[1,1] / TT
cov.alpha.21 # (4)

cov.alpha.22 <- Sig.e[2,2] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[2,2] / TT
cov.alpha.22 # (5)

cov.alpha.23 <- Sig.e[2,2] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[3,3] / TT
cov.alpha.23 # (6)


cov.alpha.31 <- Sig.e[3,3] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[1,1] / TT
cov.alpha.31 # (7)

cov.alpha.32 <- Sig.e[3,3] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[2,2] / TT
cov.alpha.32 # (8)

cov.alpha.33 <- Sig.e[3,3] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[3,3] / TT
cov.alpha.33 # (9)

```

```{r}

cov.alpha <- Sig.e %x% solve(t(beta.norm) %*% S11 %*% beta.norm) / TT

```

Compare with standard error for $\widehat{\alpha}$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(alpha.norm/matrix(sqrt(diag(cov.alpha)), nrow = 5, ncol = 3, byrow = TRUE), 2)

```



<!-- .................................................. -->
<hr>

### $\mathcal{H}_{S.2}$ in *Table 12.1* of @Juselius2006Cointegrated

Construct the design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0, 0, 0,
               -1, 0, 0, 0,
                0, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = T)

H2 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0,-1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = T)

H3 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = T)

```

Estimate the (just) identified cointegrating and adjustment coefficients.

```{r}

z <- ca.jo.res.02

b.s2.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 3)

```

Compare results for $\widehat{\beta}$ (see $\mathcal{H}_{S.2}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

beta.norm <- b.s2.res$V
round(beta.norm, 2)

```

Compare results for $\widehat{\alpha}$ (see $\mathcal{H}_{S.2}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

alpha.norm <- b.s2.res$W
round(alpha.norm, 2)

```

Compute standard error for $\widehat{\beta}$

```{r}

H <- matrix(rep(0, (3*6)*(3*4-3)), nrow = (3*6), ncol = (3*4-3))

H[( 0+1): 6,(0+1):3] <- H1[,-1]
H[( 6+1):12,(3+1):6] <- H2[,-2]
H[(12+1):18,(6+1):9] <- H3[,-2]

```

```{r}

Sig.e <- b.s2.res$z$DELTA
S11   <- b.s2.res$z$SKK

TT <- nrow(b.s2.res$z$R0)

```

```{r}

cov.beta <- H %*% solve( t(H) %*% ( (t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) %x% S11 ) %*% H ) %*% t(H) / TT

```

Compare with standard error for $\widehat{\beta}$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

matrix(round(c(beta.norm)/sqrt(diag(cov.beta)), 2), nrow = 6, ncol = 3)

```

Compute standard error for $\widehat{\alpha}$

```{r}

cov.alpha <- Sig.e %x% solve(t(beta.norm) %*% S11 %*% beta.norm) / TT

```

Compare with standard error for $\widehat{\alpha}$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated

```{r}

round(alpha.norm/matrix(sqrt(diag(cov.alpha)), nrow = 5, ncol = 3, byrow = TRUE), 2)

```



<!-- .................................................. -->
<hr>

## Over-Identified structures

### $\mathcal{H}_{S.3}$ in *Table 12.3* of @Juselius2006Cointegrated

Construct the design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0,
               -1, 0,
                0, 0,
                0, 0,
                0, 0,
                0, 1), nrow = 6, ncol = 2, byrow = TRUE)

H2 <- matrix(c( 0, 0, 0,
                1, 0, 0,
                0, 1, 0,
                0, 0, 0,
                0, 0, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

H3 <- matrix(c( 0,  0, 0,
                0,  0, 0,
                1,  0, 0,
               -1, -1, 0,
                0,  1, 0,
                0,  0, 1), nrow = 6, ncol = 3, byrow = TRUE)

```

Estimate the (over) identified cointegrating and adjustment coefficients.

```{r}

z <- ca.jo.res.02

b.s3.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 4, df = 4)

```

Compare results for $\widehat{\beta}$ (see $\mathcal{H}_{S.3}$ in *Table 12.3* of @Juselius2006Cointegrated)

```{r}

beta.norm <- b.s3.res$V
round(beta.norm, 2)

```

Compare results for $\widehat{\alpha}$ (see $\mathcal{H}_{S.3}$ in *Table 12.3* of @Juselius2006Cointegrated)

```{r}

alpha.norm <- b.s3.res$W
round(alpha.norm, 2)

```

Compare value for *LR-test* on *page 220* of @Juselius2006Cointegrated

```{r}

round(b.s3.res$teststat, 2)
round(b.s3.res$pval, 2)

```

Compute standard error for $\widehat{\beta}$

```{r, include=FALSE}

# H3 <- matrix(c( 0,  0, 0,
#                 0,  0, 0,
#                -1,  0, 0,
#                 0,  0, 0,
#                 0, -1, 0,
#                 0,  0, 1), nrow = 6, ncol = 3, byrow = TRUE)
# 
# H <- matrix(rep(0, 3*6*(2+3+3-2)), nrow = 3*6, ncol = 2+3+3-2)
# 
# H[( 0+1): 6,(0+1):1] <- H1[,-1]
# H[( 6+1):12,(1+1):3] <- H2[,-2]
# H[(12+1):18,(3+1):6] <- H3

```


```{r}

H <- matrix(rep(0, (3*6)*(2+3+3-4)), nrow = (3*6), ncol = (2+3+3-4))

H[( 0+1): 6,(0+1):1] <- H1[,-1]
H[( 6+1):12,(1+1):3] <- H2[,-2]
H[(12+1):18,(3+1):4] <- H3[,-c(1,2)]

```

```{r}

Sig.e <- b.s3.res$z$DELTA
S11   <- b.s3.res$z$SKK

TT <- nrow(b.s3.res$z$R0)

```

```{r}

cov.beta <- H %*% solve( t(H) %*% ( (t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) %x% S11 ) %*% H ) %*% t(H) / TT

```

Compare with standard error for $\widehat{\beta}$ (see $\mathcal{H}_{S.3}$ in *Table 12.3* of @Juselius2006Cointegrated)

```{r}

matrix(round(c(beta.norm)/sqrt(diag(cov.beta)), 2), nrow = 6, ncol = 3)

```

Compute standard error for $\widehat{\alpha}$

```{r}

cov.alpha <- Sig.e %x% solve(t(beta.norm) %*% S11 %*% beta.norm) / TT

```

Compare with standard error for $\widehat{\alpha}$ (see $\mathcal{H}_{S.3}$ in *Table 12.3* of @Juselius2006Cointegrated

```{r}

round(alpha.norm/matrix(sqrt(diag(cov.alpha)), nrow = 5, ncol = 3, byrow = TRUE), 2)

```



<!-- .................................................. -->
<hr>

### $\mathcal{H}_{S.4}$ in *Table 12.3* of @Juselius2006Cointegrated

Construct the design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0, 0,
               -1, 0, 0,
                0, 0, 0,
                0, 1, 0,
                0,-1, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

H2 <- matrix(c( 0, 0, 0,
                1, 0, 0,
                0, 1, 0,
                0, 0, 0,
                0, 0, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

H3 <- matrix(c( 0, 0, 0,
                0, 0, 0,
                0, 0, 0,
                1, 0, 0,
                0, 1, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

```

Estimate the (over) identified cointegrating and adjustment coefficients.

```{r}

z <- ca.jo.res.02

b.s4.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 4,
                                conv.val = 1e-10, max.iter = 100,
                                df = 3)

```

Compare results for $\widehat{\beta}$ (see $\mathcal{H}_{S.4}$ in *Table 12.3* of @Juselius2006Cointegrated)

```{r}

beta.norm <- b.s4.res$V
round(beta.norm, 2)

```

Compare results for $\widehat{\alpha}$ (see $\mathcal{H}_{S.4}$ in *Table 12.3* of @Juselius2006Cointegrated)

```{r}

alpha.norm <- b.s4.res$W
round(alpha.norm, 2)

```

Compare value for *LR-test* on *page 221* of @Juselius2006Cointegrated

```{r}

round(Re(b.s4.res$teststat), 2)
round(b.s4.res$pval, 2)

```

Compute standard error for $\widehat{\beta}$

```{r}

H <- matrix(rep(0, (3*6)*(3*3-3)), nrow = (3*6), ncol = (3*3-3))

H[( 0+1): 6,(0+1):2] <- H1[,-1]
H[( 6+1):12,(2+1):4] <- H2[,-2]
H[(12+1):18,(4+1):6] <- H3[,-1]

```

```{r}

Sig.e <- b.s4.res$z$DELTA
S11   <- b.s4.res$z$SKK

TT <- nrow(b.s4.res$z$R0)

```

```{r}

cov.beta <- H %*% solve( t(H) %*% ( (t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) %x% S11 ) %*% H ) %*% t(H) / TT

```

Compare with standard error for $\widehat{\beta}$ (see $\mathcal{H}_{S.4}$ in *Table 12.3* of @Juselius2006Cointegrated)

```{r}

matrix(round(c(beta.norm)/sqrt(diag(cov.beta)), 2), nrow = 6, ncol = 3)

```

Compute standard error for $\widehat{\alpha}$

```{r}

cov.alpha <- Sig.e %x% solve(t(beta.norm) %*% S11 %*% beta.norm) / TT

```

Compare with standard error for $\widehat{\alpha}$ (see $\mathcal{H}_{S.4}$ in *Table 12.3* of @Juselius2006Cointegrated

```{r}

round(alpha.norm/matrix(sqrt(diag(cov.alpha)), nrow = 5, ncol = 3, byrow = TRUE), 2)

```


