---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Identification of the long-run structure

```{r, include=FALSE}

source("./R/01-data.R")
source("./R/03-cointegrated-var.R")

```

This chapter contains the replication of the material of Chapter 12 of @Juselius2006Cointegrated.

## Just-identified long-run structures

<!-- .................................................. -->
<hr>

### $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated

<!-- .................................................. -->
<hr>

#### Estimates

Use the estimation result `ca.jo.res.02` and reorder the variables according to $\left(m^r, \Delta p, R_m, y^r, R_b\right)$.

<!-- Apply triangularization, i.e., normalize w.r.t. to $m^r$, $\Delta p$ and $R_m$. -->

```{r}

P <- matrix(c(1,0,0,0,0,0,
              0,0,1,0,0,0,
              0,0,0,1,0,0,
              0,1,0,0,0,0,
              0,0,0,0,1,0,
              0,0,0,0,0,1), nrow = 6, byrow = T)

beta.hat <- P %*% ca.jo.res.02$Vorg[,c(1,2,3)]

alpha.hat <- P[-6,-6] %*% ca.jo.res.02$Worg[,c(1,2,3)]

```

<!-- .................................................. -->
<hr>

Apply normalization of $\widehat{\beta}$ by $c$ (see *Chapter 13.2* of @Johansen1995Likelihood)

\begin{align}
\widehat{\beta}_{c}=\widehat{\beta}\left(c^{'}\widehat{\beta}\right)^{-1},
\end{align}

with $c^{'}=\left(I_{r}, 0_{p}\right)$.

Construct $c$

```{r}

r <- 3
c1 <- diag(r)
c2 <- matrix(0, nrow = nrow(beta.hat) - r, ncol = r)
c.norm <- rbind(c1, c2)

```

Construct $\widehat{\beta}_{c}$

```{r}

beta.norm <- beta.hat %*% solve(t(c.norm) %*% beta.hat)

```

Compare with results under $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated

```{r}

round(t(P) %*% beta.norm, 2)

```





<!-- .................................................. -->
<hr>

Apply normalization of $\widehat{\alpha}$ by $c$ (see *Chapter 13.2* of @Johansen1995Likelihood)

\begin{align}
\widehat{\alpha}_{c}=\widehat{\alpha}\widehat{\beta}^{'}c,
\end{align}

with $c^{'}=\left(I_{r}, 0_{p}\right)$.

Construct $\widehat{\alpha}_{c}$

```{r}

alpha.norm <- alpha.hat %*% (t(beta.hat) %*% c.norm)

```

Compare with results under $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated

```{r}

round(t(P[-6,-6]) %*% alpha.norm, 2)

```





<!-- .................................................. -->
<hr>

#### Standard Errors

<!-- .................................................. -->
<hr>

Construct standard errors based on *Equation 12.13* of @Juselius2006Cointegrated.

```{r}

TT <- nrow(ca.jo.res.02$R0)
nr <- nrow(beta.norm)

```

Reorder the elements in $S_{11}$, $S_{01}$ and $\widehat{\Omega}$ according to $\left(m^r, \Delta p, R_m, y^r, R_b\right)$.

```{r}

S11 <- P %*% ca.jo.res.02$SKK %*% t(P)
S01 <- P[-6,-6] %*% ca.jo.res.02$S0K %*% t(P)
Sig.e <- P[-6,-6] %*% ca.jo.res.02$DELTA %*% t(P[-6,-6])

```

<!-- .................................................. -->
<hr>

Construct design matrix for each relationship, e.g., $\widetilde{H}_1$

<!-- Relationship between $C$, $R$ and $H$. -->

<!-- Different ways to impose restrictions on $\beta_i$ -->

<!-- * In terms of restrictions using $C_i$, i.e., $C^{'}_i \beta_i = 1$ (see *page 177* of @Johansen1995Likelihood) -->
<!-- * In terms of restrictions using $R_i$, i.e., $R^{'}_i \beta_i = 0$ (see *page 175* of @Juselius2006Cointegrated.) -->
<!-- * In terms of free parameters using $H_i$, i.e., $\beta_i = H_i \varphi_i$ (see *page 174* of @Juselius2006Cointegrated.) -->

<!-- Relationship between $R_i$ and $H_i$ -->

<!-- \begin{align} -->
<!-- R_i = H_{\perp i} -->
<!-- \end{align} -->

Before normalization w.r.t. $\varphi_{11}$

\begin{align}
\beta^{c}_{1} = H_{1} \varphi_1
\end{align}

\begin{align}
H_{1} = \begin{bmatrix} 1 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \\ 0 & 0 & 0 & 0 \\ 0 & 1 & 0 & 0 \\ 0 & 0 & 1 & 0 \\ 0 & 0 & 0 & 1 \end{bmatrix} \qquad \text{and} \qquad 
\varphi_{1} = \begin{bmatrix} \varphi_{11} \\ \varphi_{21} \\ \varphi_{31} \\ \varphi_{41} \end{bmatrix}.
\end{align}

After normalization w.r.t. $\varphi_{11}$

\begin{align}
\beta^{c}_{1} = h_{1} + \widetilde{H}_{1} \widetilde{\varphi}_1
\end{align}

\begin{align}
\widetilde{H}_{1} = \begin{bmatrix} 0 & 0 & 0 \\ 0 & 0 & 0 \\ 0 & 0 & 0 \\ 1 & 0 & 0 \\ 0 & 1 & 0 \\ 0 & 0 & 1 \end{bmatrix} \qquad \text{and} \qquad 
\widetilde{\varphi}_{1} = \begin{bmatrix} \widetilde{\varphi}_{21} \\ \widetilde{\varphi}_{31} \\ \widetilde{\varphi}_{41} \end{bmatrix}.
\end{align}

with 

\begin{align}
\widetilde{\varphi}_{21} = \frac{\varphi_{21}}{\varphi_{11}}, \qquad
\widetilde{\varphi}_{31} = \frac{\varphi_{31}}{\varphi_{11}}, \qquad
\widetilde{\varphi}_{41} = \frac{\varphi_{41}}{\varphi_{11}}
\end{align}

<!-- .................................................. -->
<hr>

Combine all individual design matrices of each relationship in ${\bf \widetilde{H}}$

<!-- \begin{align} -->
<!-- {\bf \widetilde{H}} = \begin{bmatrix} {\bf \widetilde{H}_1} & 0 & \dots & 0 \\ 0 & {\bf \widetilde{H}_2} & 0 & \vdots \\ \vdots & 0 & \ddots & 0 \\ 0 & \vdots & 0 & {\bf \widetilde{H}_r} \end{bmatrix} -->
<!-- \end{align} -->

\begin{align}
{\bf \widetilde{H}} = \begin{bmatrix} \widetilde{H}_1 & 0 & \dots & 0 \\ 0 & \widetilde{H}_2 & 0 & \vdots \\ \vdots & 0 & \ddots & 0 \\ 0 & \vdots & 0 & \widetilde{H}_r \end{bmatrix}
\end{align}

```{r}

library(MASS)
H <- MASS::Null(c.norm)
H <- diag(r) %x% H

```

Construct $\widehat{\Sigma}_{\widehat{\beta}\widehat{\beta}}$

```{r}

cov.beta.jus <- H %*% solve( t(H) %*% ( (t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) %x% S11 ) %*% H ) %*% t(H) / TT

```

```{r}

se <- sqrt(diag(cov.beta.jus)[c((0*nr+r+1):(0*nr+r+r), (1*nr+r+1):(1*nr+r+r), (2*nr+r+1):(2*nr+r+r))])

```

```{r}

se.mat <- t(P) %*% rbind(diag(r), matrix(se, nrow = nr-r, ncol = r))

```

Test statistic $\widehat{\beta}_i$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(t(P) %*% beta.norm / se.mat, 2)

```



<!-- .................................................. -->
<hr>

Construct standard errors based on *Equation 13.12* of @Johansen1995Likelihood

```{r}

cov.beta <- ((diag(nr) - beta.norm %*% t(c.norm)) %*% solve(S11) %*% (diag(nr) - c.norm %*% t(beta.norm))) %x% solve(t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) / TT

se.beta <- sqrt(diag(cov.beta))
se.beta

```

$\widehat{\Sigma}_{\alpha}$

```{r}

cov.alpha.jus <- Sig.e[1,1] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[1,1] / TT

cov.alpha.jus
sqrt(cov.alpha.jus)

alpha.norm[1,1]/sqrt(cov.alpha.jus)
round(alpha.norm[1,1], 3)/round(sqrt(cov.alpha.jus), 3)

```

```{r}

cov.alpha.jus <- Sig.e[4,4] %*% solve(t(beta.norm) %*% S11 %*% beta.norm)[1,1] / TT

cov.alpha.jus
sqrt(cov.alpha.jus)

alpha.norm[4,1]/sqrt(cov.alpha.jus)
round(alpha.norm[4,1], 3)/round(sqrt(cov.alpha.jus), 3)

```

```{r}

cov.alpha.jus <- Sig.e %x% solve(t(beta.norm) %*% S11 %*% beta.norm) / TT

cov.alpha.jus
sqrt(diag(cov.alpha.jus))

xxx <- matrix(sqrt(diag(cov.alpha.jus)), nrow = 5, ncol = 3, byrow = TRUE)

alpha.norm/xxx

```


## Just-Identified structures

Load the function `ca_jo_jus06_hr3_fun()` from *GitHub*. 

```{r}

source("https://raw.githubusercontent.com/mmoessler/juselius-2006/main/R/ca_jo_jus06_hr3_fun.R")

```



### $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated

Construct design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 0, 0,
                0, 0, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = TRUE)

H2 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = TRUE)

H3 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = TRUE)

```

Estimate (just) identified cointegrating coefficients.

```{r}

z <- ca.jo.res.02
z$P <- 6

b.s1.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 4)

```

Cointegrating coefficients (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

beta.norm <- b.s1.res$V
round(beta.norm, 2)

```

Adjustment coefficients (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

alpha.norm <- b.s1.res$W
round(alpha.norm, 2)

```

Standard error for $\widehat{\beta}$

```{r}

H <- matrix(rep(0, 3*6*3*3), nrow = 3*6, ncol = 3*4-3)

H[( 0+1): 6,(0+1):3] <- H1[,-1]
H[( 6+1):12,(3+1):6] <- H2[,-2]
H[(12+1):18,(6+1):9] <- H3[,-2]

```

```{r}

Sig.e <- b.s1.res$z$DELTA
S11   <- b.s1.res$z$SKK

TT <- nrow(b.s1.res$z$R0)

```


```{r}

cov.beta <- H %*% solve( t(H) %*% ( (t(alpha.norm) %*% solve(Sig.e) %*% alpha.norm) %x% S11 ) %*% H ) %*% t(H) / TT

```

Standard error for cointegrating coefficients (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

matrix(round(c(beta.norm)/sqrt(diag(cov.beta)), 2), nrow = 6, ncol = 3)

```







```{r}

se.mat <- t(P) %*% rbind(diag(r), matrix(se, nrow = nr-r, ncol = r))

```

Test statistic $\widehat{\beta}_i$ (see $\mathcal{H}_{S.1}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(t(P) %*% beta.norm / se.mat, 2)

```




### $\mathcal{H}_{S.2}$ in *Table 12.1* of @Juselius2006Cointegrated

Construct design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0, 0, 0,
               -1, 0, 0, 0,
                0, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = T)
H2 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0,-1, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = T)
H3 <- matrix(c( 0, 0, 0, 0,
                1, 0, 0, 0,
                0, 1, 0, 0,
                0, 0, 1, 0,
                0, 0, 0, 0,
                0, 0, 0, 1), nrow = 6, ncol = 4, byrow = T)

```

Estimate (just) identified cointegrating coefficients.

```{r}

z <- ca.jo.res.02
z$P <- 6

b.s2.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 3)

```

Results for (just) identified cointegrating coefficient (see $\mathcal{H}_{S.2}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(b.s2.res$bet.nor, 2)

```





## Over-Identified structures

### $\mathcal{H}_{S.3}$ in *Table 12.3* of @Juselius2006Cointegrated

Construct design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0,
               -1, 0,
                0, 0,
                0, 0,
                0, 0,
                0, 1), nrow = 6, ncol = 2, byrow = TRUE)

H2 <- matrix(c( 0, 0, 0,
                1, 0, 0,
                0, 1, 0,
                0, 0, 0,
                0, 0, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

H3 <- matrix(c( 0,  0, 0,
                0,  0, 0,
                1,  0, 0,
               -1, -1, 0,
                0,  1, 0,
                0,  0, 1), nrow = 6, ncol = 3, byrow = TRUE)

```

Estimate (just) identified cointegrating coefficients.

```{r}

z <- ca.jo.res.02
z$P <- 6

b.s3.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 4)

```

Results for (over) identified cointegrating coefficient (see $\mathcal{H}_{S.3}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(b.s3.res$bet.nor, 2)

```


### $\mathcal{H}_{S.4}$ in *Table 12.3* of @Juselius2006Cointegrated

Construct design matrices $H_i$ for $i=1,2,3$.

```{r}

H1 <- matrix(c( 1, 0, 0,
               -1, 0, 0,
                0, 0, 0,
                0, 1, 0,
                0,-1, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

H2 <- matrix(c( 0, 0, 0,
                1, 0, 0,
                0, 1, 0,
                0, 0, 0,
                0, 0, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

H3 <- matrix(c( 0, 0, 0,
                0, 0, 0,
                0, 0, 0,
                1, 0, 0,
                0, 1, 0,
                0, 0, 1), nrow = 6, ncol = 3, byrow = TRUE)

```

Estimate (just) identified cointegrating coefficients.

```{r}

z <- ca.jo.res.02
z$P <- 6

b.s4.res <- ca_jo_jus06_hr3_fun(z = z,
                                H1 = H1, H2 = H2, H3 = H3,
                                nor.id1 = 1, nor.id2 = 3, nor.id3 = 4,
                                conv.val = 1e-10, max.iter = 1000)

```

Results for (over) identified cointegrating coefficient (see $\mathcal{H}_{S.3}$ in *Table 12.1* of @Juselius2006Cointegrated)

```{r}

round(b.s4.res$bet.nor, 2)

```



